Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-25 paper/paper.tex
new figure

@@

We select for further analysis the best $1\%$ models according to the
lowest $\chi^2$ values.
We note that the difference between the lowest and highest $\chi^2$ values in
those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
$\chi^2$ being close to $\chi^2_{min}=1200$. To have a sense of scale,
the total number of degrees of freedom is $104$.

Then we perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
distribution in the best $25$ models against the parent distribution
of $2500$ models. 
If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
this parameter does influence the $\chi^2$ fit, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.

The best values for the influential parameters correspond to
the values that produce the minimum
$\chi^2$.
We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
$\chi^2$ as a function of the influential parameters around its
corresponding minimum.   
%$v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
%$P_{\rm cl}$

@@

From the K-S tests we find that only three parameters can be
constrained by the observations: the clump outflow velocity
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), the clump velocity
dispersion $\sigma_{\rm cl}$ (p-value $10^{-4}$) and the probability
that the \lya\ emission comes from the clumps $P_{\rm cl}$ (p-value
$10^{-4}$).
This does not mean the other parameters do not influence the resulting
spectra at all; it means that they cannot be constrained from \tol's
observations.

The results are summarized in Figure \ref{multiphaseresults}.
Left panels show the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2$. 
The right panel shows the actual $\chi^2$ values (normalized by the
degrees of freedom) and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

We tested with a set of 100 additional Monte-Carlo simulations
with random values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$ and
$P_{\rm cl}$ within the derived constraints (and random values for the
other parameters over the whole parameter range) and found that $30$
models result in $\chi^2$ values  
continue to provide a similar $\chi^2$ values as the best $25$ models.

@@

Having constrained only 3 parameters, one migh wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Event if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{tree_result.pdf}
\caption{Classification tree example. 
The aim is to find the parameters that separate two
classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
Each box describes the condition over the parameter of interest, the
level of sample impurity, the number of samples and the value of the
number of samples in each classes.  
In this example we start with $28$ models in the first class and
$1962$ models in the second class; the best way to increase the probability to find a
a result with low $\chi^2/d.o.f.$ ($13$ models) is having $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
All other parameters are also importatn but these three are the most relevant.
\label{fig:tree}}
\end{center}
\end{figure*}

@@

We select for further analysis the best $1\%$ models according to the
lowest $\chi^2$ values.
We note that the difference between the lowest and highest $\chi^2$ values in
those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
$\chi^2$ being close to $\chi^2_{min}=1200$. 
The total number of degrees of freedom, $d.o.f$, is $104$.

We divide the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.35>$.
We apply a random forest classification algorithm to find the
parameters more relevant in splitting the results into these two
classes. The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for tability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as a
training set.

We also perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
distribution in the best $25$ models against the parent distribution
of $2500$ models. 
If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
this parameter does influence the $\chi^2$ result, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.

We finally compute the best values for the influential parameters as
the values that produce the minimum $\chi^2$.  
We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
$\chi^2$ as a function of the influential parameters around its
corresponding minimum.

@@

With $14$ free parameters our first concern is discovering which are
the most relevant in reproducing \tol's line shape.
The results of the random forest classifier yield that the clump outflow velocity
$v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
that the \lya\ emission comes from the clumps $P_{\rm cl}$ are the
most influential parameters in finding a model with low
$\chi^2/d.o.f.$.

Figure \ref{fig:tree} shows the results for one of such tree. 
Starting with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes respectively, we find that the best separation
yields $13$ and $44$ models after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
The split is not perfect. This means that the three parameters in the
model are the most influential, but that some combinations of the
other 11 parameters are also relevant to find a good fit.

From the K-S tests we confirm that the same three parameters are the
only ones that can be constrained by observations;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
Once again, this test does not mean the other parameters do not
influence the resulting spectra at all; it means that they cannot be
constrained from \tol's observations.

The best models are summarized in Figure \ref{multiphaseresults}.
Left column show the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2/d.o.f.$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

As a test, we ran a small set of 100 additional Monte-Carlo simulations
with random values for all parameters, except for $\sigma_{\rm cl}$,
$v_{\infty {\rm cl}}$, $P_{\rm cl}$ which where within the derived
constraints.
Consistent with the results from the random forest algorithm,
illustrated by the classification tree of Figure \ref{fig:tree}, we
found that $30$ models showed $\chi^2/d.o.f.<35$ values

@@

Having constrained only 3 parameters, one migh wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Event if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3.
